I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-08 Paper/Paper_noProof.tex
Writing

In our experiments, we only consider the paths of length 3 (the source node is 2 layers before) and length 4 (the source node is 3 layers before). We will dynamically adjust the values during the process of node chosen.

\subsubsection*{Pseudocode}

The following needs a chart of pseudo-code

@@

\begin{algorithm}
	\caption{Process for length 3 + length 4}
	\KwData{Input data}
	\KwResult{Open node list}
	\While{condition}{
		Perform operation 1\;
		\If{condition}{
			Perform operation 2\;
		}
		\Else{
			Perform operation 3\;
		}
	}
\end{algorithm}

@@

We explain our framework in 4 subsections: precomputation, process for one image, process for one node, and global process.

@@

\vspace*{-8ex}

@@

	\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
\end{tabular}
\caption{The data of verified accuracy (\%) and average time (s) of 1000 images evaluated on the PRIMA and on the beta-Crown are in CITE.}
\label{tab:example}
\end{table}

>>>>

In our experiments, we only consider the paths of length 3 (the source node is 2 layers before) and length 4 (the source node is 3 layers before). We will dynamically adjust the values during the process of node chosen. In text, the process of node chosen for length 3 plus length 4 is as follows:

@@

And the pseudo-code is as follows:

\begin{algorithm}
	\caption{Process for length 3 + length 4}
	\KwData{Sorted lists of length 3 + length 4}
	\KwResult{Open node list}

	Let $N = 0$ be the number of Chosen length 4 pair.

	\While{len(Open node) $<O$}{
		Pick the first element $P_3$ in the list of length 3\;

		Let $V_3$ be the value of $P_3$\;

		Pick the first element $P_4$ in the list of length 4\;

		Let $V_4$ be the value of $P_4$\;

		\If{$V_3 > V_4 \cdot N$}{
			Add nodes in $P_3$ into Open list\;
			Number of Chosen lentgh pair $N$ += 1\; 
		}
		\Else{
			Add nodes in $P_4$ into Open list\;
		}
	}
\end{algorithm}

@@

In this section, We will explain our framework in 4 subsections: precomputation, process for one image, process for one node, and global process.

@@

@@

		\textrm{MLP}\ 8$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

		\textrm{MLP}\ 5$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

		\textrm{MLP}\ 8$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

		\textrm{MLP}\ 6$\times$500\  &   0.035& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
	\end{tabular}
	\caption{The data of verified accuracy (\%) and average time (s) of 1000 images evaluated on the PRIMA and on the beta-Crown are in CITE.}
	\label{tab:example}
\end{table}

On all 4 networks, our fast version can exceed PRIMA both in accuracy and speed. On all 4 networks, our slow version can have a similar verified accuracy as beta-Crown.
